E Coli Project Paper Incredibly Rough Draft

### 2013-08-30 paper/paper.tex
merge with Rene and also moved wall summing loop in protein_microscopy.cpp Tested everything on crystal.

@@

@@

@@

>>>>

With arrow plots - have noticed that the wall attached proteins seem
to climb along the walls with little arrows, so the maxima crawl
along, in a way.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-plot-D_ND-randst-25-800-600-9700-1500}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-plot-D_E_NDE-randst-25-800-600-9700-1500}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-plot-E_nE-randst-25-800-600-9700-1500}
  \caption{Arrows that connect maxima that are global in space and
    local in time. The arrow heads touch spatial, time maxima and are
    adjecent to the tails of arrows that show the very next spatial,
    time maxima. The proteins shown are wall attached MinD-ATP (top),
    wall attached MinD-MinE-ATP (middle), and cytoplasmic MinE (bottom).}
  \label{arrow-plot-randst-97-plot}
\end{figure}

Figure \ref{arrow-plot-randst-97-plot} shows three arrow plots for
this shape of cell.  It's interesting that wall attached MinD never
have global maxima in the middle flat region of the cell while both
forms of MinE, the cytoplasmic MinE and the wall attached
MinD-MinE-ATP, have a number of maxima in this region of the cell.  It
seems that the MinE never stray far from the middle of the cell - they
approach the ends and react with the other proteins, sticking for a
while on the walls.  In order for a cytoplasmic MinE to reach the very
end, it must pass a large amount of opportunity to react with MinD.
\fixme{I stopped writing this reasoning because I'm not sure it's
  valid.  Interesting thoug.  Look at this more.}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-plot-D_ND-randst-25-600-800-9800-1500}
  \caption{Arrows that connect maxima that are global in space and
    local in time. The arrow heads touch spatial, time maxima and are
    adjecent to the tails of arrows that show the very next spatial,
    time maxima. The protein that is shown is wall attached MinD-ATP.}
  \label{arrow-plot-randst-98-plot}
\end{figure}

The arrow plot shown here is typical of mannik's squished adnormal
shape.  It shows the protein maxima moving through the cell from one
end to the other end, and back again.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-plot-D_nATP-randst-25-600-600-9900-1500}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-plot-D_nADP-randst-25-600-600-9900-1500}
  \caption{Arrows that connect maxima that are global in space and
    local in time. The arrow heads touch spatial, time maxima and are
    adjecent to the tails of arrows that show the very next spatial,
    time maxima. The proteins shown are cytopasmic MinD-ATP (above) and MinD-ADP (below).}
  \label{arrow-plot-randst-99-plot}
\end{figure}
Figure \ref{arrow-plot-randst-99-plot} shows maxima that are global in
space and local in time.  It is interesting that the MinD-ATP, the
stage that immediately proceeds attachement to the wall, show maxima
in one base corner of the A shape and then immediate maxima in the
other base corner, skipping any maxima steps in the middle (the top of
the A), while the MinD-ADP, the stage that has just left the wall,
shows no such behavoir.  Every base corner maxima is followed by a top
corner maxima, with very obvious symmetry.
